R Notebook

### 2017-04-11 doc/RMD/MLG-distribution.Rmd
update SVG images to not be too dang tall

```{r graph-16-loci, fig.width = 7, fig.height = 7}
par(mfrow = c(1, 1))
(g16o <- cluster_optimal(graph16loc$total))
plot_mlg_graph(graph16loc$total, alt_layout) + labs(list(subtitle = "(16 loci)"))
ggsave(filename = "results/figures/publication/FigureS1Z.svg", width = 88, units = "mm", scale = 2)
```

@@

```{r graph-11-loci, fig.width = 7, fig.height = 7}
(g11o <- cluster_optimal(graph11loc$total))
plot_mlg_graph(graph11loc$total, alt_layout) + labs(list(subtitle = "(11 loci)"))
ggsave(filename = "results/figures/publication/Figure3Z.svg", width = 88, units = "mm", scale = 2)
```

>>>>

```{r graph-16-loci, fig.width = 7, fig.height = 7}
par(mfrow = c(1, 1))
(g16o <- cluster_optimal(graph16loc$total))
plot_mlg_graph(graph16loc$total, alt_layout) + labs(list(subtitle = "(16 loci)"))
ggsave(filename = "results/figures/publication/FigureS1Z.svg", width = 88, height = 88, units = "mm", scale = 2)
```

@@

```{r graph-11-loci, fig.width = 7, fig.height = 7}
(g11o <- cluster_optimal(graph11loc$total))
plot_mlg_graph(graph11loc$total, alt_layout) + labs(list(subtitle = "(11 loci)"))
ggsave(filename = "results/figures/publication/Figure3Z.svg", width = 88, height = 88, units = "mm", scale = 2)
```
